\documentclass[a4paper, 10pt]{article}
\usepackage[margin=3cm]{geometry}
\usepackage{helvet}

\usepackage{hyperref}
\hypersetup{
   colorlinks,
   citecolor=black,
   filecolor=black,
   linkcolor=black,
   urlcolor=blue
}

\usepackage{url}
\usepackage{bibentry}

% Reformat the date
% http://www.howtotex.com/packages/customize-the-date-format-in-your-latex-documents/
% \usepackage{datetime}
% \newdateformat{mydate}{\THEYEAR\ \monthname[\THEMONTH] \THEDAY\textsuperscript{th}}

% \author{
%    \href{mailto:viv3kanand@gmail.com}{viv3kanand@gmail.com}
% }
% \date{\mydate\today}

% remove date and whitespace from title
\date{\vspace{-10ex}}

\usepackage{array, xcolor}
\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

\begin{document}
% remove space above title
\title{\vspace{-12ex}Vivekanand A}

\maketitle

\parbox[t]{0.5\textwidth}{
\begin{tabbing}
\hspace{3cm} \= \hspace{4cm} \= \kill
{\bf Address} \> Thulasitharayil, \\
\> Thattamala P.O, \\
\> Kollam, 691020\\
\> Kerala, India. \\
{\bf Date of Birth} \> 1990 June 25\textsuperscript{st} \\
{\bf Nationality} \> Indian \\
\end{tabbing}
}
\hfil
\parbox[t]{0.5\textwidth}{
\begin{tabbing}
\hspace{2cm} \= \hspace{4cm} \= \kill
{\bf GitHub} \> \href{https://github.com/viv3kanand}{https://github.com/viv3kanand} \\
%{\bf Twitter} \> \href{https://twitter.com/viv3kanand}{https://twitter.com/viv3kanand} \\
{\bf Email} \> \href{mailto:viv3kanand@gmail.com}{viv3kanand@gmail.com} \\
{\bf Phone} \> +91 9496819723
\end{tabbing}
}

%\section*{Summary}





\section*{Education}
\begin{tabular}{L!{\VRule}R}
   2011--2013 & MSc. Bioinformatics, Amrita VishwaVidyapeetham, Amritapuri Campus, \\
& \ Kerala. Percentage of Marks: 66 \\
   2008--2011 & BSc. Microbiology, Amrita VishwaVidyapeetham, Amritapuri Campus, \\
& \ Kerala. Percentage of Marks: 60 \\
\end{tabular}

\section*{Past Scientific Positions}
\begin{tabular}{L!{\VRule}R}
   2017--2018 & Research Fellow at \textbf{Indian Institute of Technology}, Delhi, India \\
   2017--2017 & Research Assistant at \textbf{Indian Institute of Science}, Bengaluru, India \\
   2014--2017 & Research Fellow at \textbf{Rajiv Gandhi Centre for Biotechnology}, India \\
\end{tabular}

 \section*{Research Interests}
 
 \begin{itemize}
    \setlength\itemsep{0em}
    \item Investigating the potential role of genetic variants in relation to biological function and disease.
    \item Genomics and transcriptomics; in particular the study of Super-enhancers, non-coding RNAs, RNA-binding proteins and transposable elements.
    \item The application of bioinformatics using Next Generation Sequencing and statistical data analysis methods to answer biological problems.
 \end{itemize}

\section*{Bioinformatic Skills}

\begin{itemize}
   \setlength\itemsep{0em}
   \item Data analysis of high-throughput sequencing data including DNA-seq, RNA-seq, CAGE-seq, ChIP-seq, Microarray and Array-CGH.
   \item Experience in sequence analysis for detecting high confidence motifs statistically (Fisher\textsc{\char13}s Exact, in reference to peer reviewed publication no. 2).
   \item Experience in extensive bio-curation and perl programming (In reference to peer reviewed publication no. 2 and 3).
   \item Proficiency in working with Python and Bio-python in pattern matching of RNA binding proteins and miRNA targeting studies.
   \item Knowledge and the ability to use various bioinformatic databases, APIs, repositories, and tools.
   \item Ability to implement bioinformatic pipelines using pipelining tools.
\end{itemize}

\section*{Computer Skills (Proficiency ordered from left to right)}

\begin{itemize}
   \setlength\itemsep{0em}
   \item Operating systems: Linux/Unix (RHEL/CentOS and Ubuntu), OS X, and Windows
   \item Programming/scripting languages: R, Perl, Python, Bash, SQL, PHP and Matlab
   \item Reproducible research tools: Git, Cloud computing (AWS and Digital Ocean), Markdown, and R Markdown
\end{itemize}

\section*{Honours and Awards}
\begin{tabular}{L!{\VRule}R}
   2016 & Selected candidate for Sakura Science Program (Japan Asia Youth Exchange Program in Science) hosted by Japan Science and Technology (JST) at Okayama University, Japan. \\
   2015 & Awarded International Travel Grant from Department of Biotechnology, India to attend a conference, RECOMB-15 held at Warsaw, Poland. \\
   2014 & Organizing member in NGS- 15, Next Generation Sequencing Data Analysis Workshop hosted by EMBL-EBI and Rajiv Gandhi Centre for Biotechnology, Thiruvananthapuram, Kerala, India. \\
\end{tabular}

\section*{Mentoring and Teaching experience}
\begin{tabular}{L!{\VRule}R}
   2017--2018 & Experience as Teaching Assistant for B-Tech/M-Tech/Ph.D. students at IIT Delhi. \\
   2014--2017 & Teaching faculty for Bioinformatics Internship Program at Rajiv Gandhi Centre for Biotechnology. \\
   2014--2017 & Teaching faculty for Bioinformatics coursework for Ph.D. students at Rajiv Gandhi Centre for Biotechnology. \\
   2014--2017 & Training faculty in Next Generation Sequencing Analysis and Perl-Python workshop series organized by Rajiv Gandhi Centre for Biotechnology. \\
\end{tabular}

\section*{Seminars, Workshops and Conference Attendances}
\begin{tabular}{L!{\VRule}R}
   2016 & Cancer Proteogenomics Workshop hosted by Broad Institute of MIT and Harvard and Rajiv Gandhi Centre for Biotechnology, held at Thiruvananthapuram, Kerala, India. \\
   2015 & Vivekanand A, Rajesh Raju, Sreenivas KP, Reshmi G, Pillai R. ``Regulatory Map of Deptor" at IACR (Indian Association of Cancer Research), held at Jaipur, Rajasthan, India. \\
   2015 & Vivekanand A, Reshmi G and Pillai MR. ``miRBP: An architecture to find competitive interaction between microRNA and RNA binding proteins" at RECOMB- 15, 19thAnnual International Conference on Research in Computational Molecular Biology, held at Warsaw, Poland. \\
   2014 & NGS- 15, Next Generation Sequencing Data Analysis Workshop hosted by EMBL-EBI and Rajiv Gandhi Centre for Biotechnology, Thiruvananthapuram, Kerala, India. \\
   2012 & NANOBIO 2012: Second International Conference on Nanotechnology, Amrita Institute of Medical Sciences, Cochin, Kerala, India. \\
   2011 & Proteomics and Genomics workshop organized by Institute of Bioinformatics, Bangalore and Amrita VishwaVidyapeetham, Amrita School of Biotechnology, Amritapuri, Kerala, India. \\
\end{tabular}



%\section*{Hobbies and Interests}
%Sports (especially football), cycling, blogging, reading, and movies.

\section*{Academic References}

\begin{minipage}[ht]{.50\textwidth}
Dr. Reshmi G \\
Former Scientist \\
Rajiv Gandhi Centre for Biotechnology, \\
%  \href{https://www.researchgate.net/profile/Reshmi_Girijadevi}{https://www.researchgate.net/profile/Reshmi_Girijadevi} \\
Thiruvananthapuram, Kerala 695014 \\
% India \\
\href{mailto:reshmisuresh@gmail.com}{reshmisuresh@gmail.com} \\
Phone: +91 9947262407
\end{minipage}
\begin{minipage}[ht]{.50\textwidth}
Dr. Vinod Chandra S. S. \\
Director, Computer Centre, \\
University of Kerala \\
%  \href{http://vinod.mirworks.in/home.php}{http://vinod.mirworks.in/home.php} \\
Thiruvananthapuram, Kerala 695034\\
\href{mailto:vinod@keralauniversity.ac.in}{vinod@keralauniversity.ac.in} \\
Phone: +91 471-2305801
\end{minipage} \newpage


\section*{Peer Reviewed Publications and Book Chapters}
% http://tex.stackexchange.com/questions/22645/hiding-the-title-of-the-bibliography

\begin{enumerate}
  \item Bijesh George, \underline{Vivekanand Ashokachandran}, Aswathy Mary Paul, Reshmi Girijadevi, ``Transcriptome Sequencing for Precise and Accurate Measurement of Transcripts and Accessibility of TCGA for Cancer Datasets and Analysis", \textbf{InTech publications}, 2016, December ISBN 978-953-51-5452-5 (Book chapter)
  \item Kandala DT, Mohan N, \underline{Asokachandran V}, Sudheesh AP, Girijadevi R, Laishram RS. ``CstF-64 and 3'-UTR cis-element determine Star-PAP specificity for target mRNA selection by excluding PAPα," \textbf{Nucleic Acids Res.}, 2016 Jan 29; 44(2):811-23
  \item Raju R, Paul AM, \underline{Asokachandran V}, George B, Radhamony L, Vinaykumar M, Girijadevi R, Pillai MR. ``The Triple-Negative Breast Cancer Database: an omics platform for reference, integration and analysis of triple-negative breast cancer data". \textbf{Breast Cancer Res.}, 2014 Dec 4; 16(6):490
  \item Vinitha A, Kutty VR, \underline{Vivekanand A}, Reshmi G, Divya G, Sumi S, Santosh KR, Pratapachandran NS, Ajit MS, Kartha CC, Ramachandran S. ``PPIA rs6850: A $>$ G single- nucleotide polymorphism is associated with raised plasma cyclophilin A levels in patients with coronary artery disease". \textbf{Mol Cell Biochem.}, 2016 Jan; 412(1-2):259-68
\end{enumerate}



%\begingroup
%   \renewcommand{\section}[2]{}
%   \bibliographystyle{unsrturl}
%   \nocite{*}
%   \bibliography{pub}
%\endgroup

\vfill

\footnotesize
%This C.V. was prepared in \LaTeX\ and is available at \href{https://github.com/viv3kanand/CV}{https://github.com/viv3kanand/CV}.

\end{document}
